---
title: "Project"
author: "Jan Cap"
date: "2022-09-05"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, results=FALSE, error=FALSE}
library(ggplot2)
library(ggcorrplot)
library(caret)

```
## Training

First, we will load data and do some research about columns. 

```{r}

train <- read.csv('project-training.csv')

na_count <-sapply(train, function(y) sum(length(which(is.na(y)))))
data.frame(na_count)
```

We can see, that all columns with NA values have many NA. We will drop those columns and column with date. From original 160 columns, we have now 92 columns.

```{r}
train_cleared <- train[ , colSums(is.na(train)) == 0]
train_cleared <- subset(train_cleared,  select = -cvtd_timestamp)

#sapply(lapply(train_cleared, unique), length)
```




```{r, echo=FALSE, results=FALSE}
unique(train_cleared$cvtd_timestamp)

names(train_cleared)
```
Lets see, how predicted value looks like.
We can see, that columns starts with "kurtosis" and "skewness" are mostly empty strings. We are gonna use just columns with x, y, z postfix, "user_name" and predicated column "classe".
```{r}
filter <- grepl( "x$|y$|z$|user_name|classe" , names( train_cleared ) )

train_num <- train_cleared[, filter]
```


It's classification problem with 5 classes. I'm gonna use knn with k=5.
```{r}
set.seed(125)
ctrl <- trainControl(method = 'cv', number = 5, savePredictions = TRUE)
model <- train(factor(classe) ~ . , data=train_num, method = "knn", trControl = ctrl, tuneGrid = data.frame(k=5))

model

```

## Predict 20 records

Here is my prediction for 20 records from test data.
```{r pressure}
test <- read.csv('project-testing.csv')
test <- test[names(train_num)[-38]]

predict(model, test)
```

```{r, echo=FALSE}
# I tried tree, with default tuning parameters and output was really bad.
#tree:
#A A A A A D D D A A A D D A D A A D A A
#knn - k=15:
#B A B A A E D B A A C C A A D A A B B B
#knn - k=5
#B A B A A E D B A A B C B A E E A B B B

#correct:
#B A B A A E D B A A - C - A - - A B B B
```

